Finite Property Convex Elicitation Notes

### 2018-05-07 cvx-fin-notes.tex
note to self
Added one question to notes and visualization for 2d elicitation

\raf{TODO: finish proof that $L'$ elicits $\Gamma'$.  $\Gamma' \supseteq \Gamma \cap \R'$ is easy.}
  Finally, let $L' = L|_{\R'}$, that is, $L':\R'\to\reals^\Y$, $L:r'\mapsto L(r')$.
  \jessiet{What is this notation?}\raft{Restricted to; clarified now I hope.}
  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot~L(r)$ $ \argmin_{r\in\R'} p\cdot~L'(r') $
\end{proof}
Note that non-degeneracy is necessary to make Lemma~\ref{lem:trim} interesting, as otherwise $\Gamma' : p \mapsto \emptyset$ would always suffice.

@@

\begin{definition}
  We say a loss $L$ is \emph{finite-piecewise-linear and convex (FPLC)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, and is bounded from below.
\end{definition}

@@

>>>>

\raf{TODO: finish proof that $L'$ elicits $\Gamma'$.  $\Gamma' \supseteq \Gamma \cap \R'$ is easy.}
  Finally, let $L' = L|_{\R'}$, that is, $L':\R'\to\reals^\Y$, $L:r'\mapsto L(r')$.
  We have $r' \in \Gamma(p) \implies r' \in \argmin_{r\in\R} p\cdot~L(r)$ $ \argmin_{r\in\R'} p\cdot~L'(r') $
\end{proof}
Note that non-degeneracy is necessary to make Lemma~\ref{lem:trim} interesting, as otherwise $\Gamma' : p \mapsto \emptyset$ would always suffice.

@@

\begin{definition}
  We say a loss $L$ is \emph{finite-piecewise-linear and convex (FPLC)} if for all $y\in\Y$, the function $L(\cdot)_y$ is a piecewise-linear function with finitely many pieces, and is bounded from below.
\jessie{Is bounded from below sufficient?  Couldn't you have FPL that looks like a roughly sketched 4th degree polynomial (two minima)-- bounded from below, but not convex.}
\end{definition}

@@

\raf{Note to self: (1) focus on distributions of full support to characterize the minimizers, (2) try to directly generalize 1d ``extreme'' points to the boundary of $C$.}
